hormones

### 2020-02-09 analysis/07_hormones.Rmd
new hormone stuff

```{r wrangle-steroids}
PETC <- read_excel("../results/hormones.xlsx", sheet = 1)  %>% 
              dplyr::rename(corticosterone = cort, progesterone = p4,
                            estradiol = e2,  testosterone = t) %>% 
               dplyr::mutate(treatment = fct_recode(treatment...3,
                            "inc.d17" = "incd17",
                            "inc.d3" = "incd3",
                            "inc.d9" = "incd9",
                            "m.inc.d9" = "minc9",
                            "m.inc.d3" = "minc3",
                            "m.inc.d8" = "minc8",
                            "m.inc.d17" = "minc17",
                            "m.n2" = "m hatch",
                            "control" = "baseline")) %>%
                dplyr::filter(treatment %in% alllevels2) %>%   
                dplyr::mutate(sex = fct_recode(sex,
                            "female" = "f",
                            "male" = "m"),
                       study = fct_collapse(treatment,
                                characterization = charlevels,
                                manipulation = maniplevels1)) %>% 
              dplyr::mutate(bird_id = gsub("[[:punct:]]", "." , id)) %>% 
              dplyr::select(bird_id, treatment, sex, study, 
                            corticosterone, estradiol, testosterone, progesterone) %>% 
              pivot_longer(cols = corticosterone:progesterone,
                           names_to = "hormone", values_to = "plasma_conc",
                           values_drop_na = TRUE) %>% 
              drop_na() %>% droplevels()  
head(PETC)
```

@@

write.csv(hormones, "../results/hormones.csv", row.names = F)

@@

# for facet wrapping
hormones <- left_join(hormones, birds)

hormones$treatment <- factor(hormones$treatment, levels = alllevels)

hormones$hormone <- factor(hormones$hormone, 
                           levels = c("prolactin", "corticosterone", "progesterone", 
                                      "estradiol", "testosterone"))
hormones$logconc <- log10(hormones$plasma_conc)
head(hormones)
```

@@

```{r savefiles}
write.csv(meanTE, "../results/07_meanTE.csv", row.names = F)
write.csv(hormones, "../results/07_hormones.csv", row.names = F)
write.csv(hormoneswide, "../results/07_hormoneswide.csv", row.names = F)
```

>>>>

```{r wrangle-steroids}
PETC <- read_excel("../results/hormones.xlsx", sheet = 1)  %>% 
              dplyr::rename(corticosterone = cort, progesterone = p4,
                            estradiol = e2,  testosterone = t) %>% 
               dplyr::mutate(treatment = fct_recode(treatment...3,
                            "inc.d17" = "incd17",
                            "inc.d3" = "incd3",
                            "inc.d9" = "incd9",
                            "m.inc.d9" = "minc9",
                            "m.inc.d3" = "minc3",
                            "m.inc.d8" = "minc8",
                            "m.inc.d17" = "minc17",
                            "m.n2" = "m hatch",
                            "control" = "baseline")) %>%
                dplyr::filter(treatment %in% alllevels2) %>%   
                dplyr::mutate(sex = fct_recode(sex,
                            "female" = "f",
                            "male" = "m"),
                       study = fct_collapse(treatment,
                                characterization = charlevels,
                                manipulation = maniplevels1),
                       moltbin = as.integer(moltbin)) %>% 
              dplyr::mutate(bird_id = gsub("[[:punct:]]", "." , id)) %>% 
              dplyr::select(bird_id, treatment, sex, study, 
                            corticosterone, estradiol, testosterone, progesterone, moltbin) %>% 
              pivot_longer(cols = corticosterone:moltbin,
                           names_to = "hormone", values_to = "plasma_conc",
                           values_drop_na = TRUE) %>% 
              drop_na() %>% droplevels()  
head(PETC)
```

@@

@@

# for faceting
hormones <- hormones %>% filter(hormone != "moltbin")
hormones$treatment <- factor(hormones$treatment, levels = alllevels)
hormones$hormone <- factor(hormones$hormone, 
                           levels = c("prolactin", "corticosterone", "progesterone", 
                                      "estradiol", "testosterone"))
# for stats
hormones$logconc <- log10(hormones$plasma_conc)
head(hormones)
```

@@

```{r savefiles}
write.csv(meanTE, "../results/07_meanTE.csv", row.names = F)
write.csv(hormones, "../results/07_hormones.csv", row.names = F)
write.csv(hormoneswide, "../results/07_hormoneswide.csv", row.names = F)

#write.csv(hormones, "../../parentalhormones/data/hormones.csv", row.names = F)
#write.csv(hormoneswide, "../../parentalhormones/data/hormoneswide.csv", row.names = F)
```
